### 2013-07-09 Rcode/intro.rmd

As an important special case, we intend these methods to address the "multiple comparisons" problem, where interest usually focuses on which $\beta_j$ can be confidently inferred to be non-zero. Such problems are usually tackled by computing a $p$ value for each $j$, often by applying a $t$ test to $\hat\beta_j/s_j$,
and then applying a generic procedure, such as that of Benjamini 
and Hochberg (1995?) or Storey (2001?), designed to control or
estimate the false discovery rate (FDR) or the positive FDR (Storey, 2001?). In essence we aim to provide analagous
generic methods that work directly with two numbers for each 
measurement $(\hat\beta_j,s_j$), rather than a single number (e.g.~ the $p$ value, or $t$ statistic). Working with these two numbers has two important benefits: first, it permits estimation and not only testing; second, the 
uncertainty in each measurement $\hat\beta_j$ can be more fully accounted for, reducing the impact of ``high-noise" measurements (large $s_j$) that can reduce the effectiveness of a standard FDR analysis. The potential for shrinkage-based estimation to
help address multiple comparisons problems has been highlighted
previously, including Greenland and Robins (1991),
Efron (2008) and Gelman et al (2012). [Note, check also Louis, JASA, 1984]

>>>>

As an important special case, these methods address the "multiple comparisons" setting, where interest focuses on which $\beta_j$ can be confidently inferred to be non-zero. Such problems are usually tackled by computing a $p$ value for each $j$, often by applying a $t$ test to $\hat\beta_j/s_j$,
and then applying a generic procedure, such as that of Benjamini 
and Hochberg (1995?) or Storey (2001?), designed to control or
estimate the false discovery rate (FDR) or the positive FDR (Storey, 2001?). In essence we aim to provide analagous
generic methods that work directly with two numbers for each 
measurement $(\hat\beta_j,s_j$), rather than a single number (e.g.~ the $p$ value, or $t$ statistic). Working with these two numbers has two important benefits: first, it permits estimation and not only testing; second, the 
uncertainty in each measurement $\hat\beta_j$ can be more fully accounted for, reducing the impact of ``high-noise" measurements (large $s_j$) that can reduce the effectiveness of a standard FDR analysis.

The potential for shrinkage-based estimation to
address the multiple comparisons setting 
has been highlighted
previously, including Greenland and Robins (1991),
Efron (2008) and Gelman et al (2012). [Note, check also Louis, JASA, 1984]

Performing multiple comparisons, or multiple tests, is often
regarded as a "problem". However, here we regard it instead as an opportunity - an opportunity to combine (or "pool") information across tests or comparisons.

Imagine that you are preparing to perform 1 million tests,
each based on a $Z$ score that is assumed to be $N(0,1)$ under the null.
You first order these tests randomly, and begin by 
performing the first test, which returns a $Z$ score of 4.
At this point you are interrupted by a friend, who asks how the analysis is going. "It's early days, but looking promising" you reply. Well, who wouldn't? If the aim is to find lots of significant differences, a strong first result is surely a good outcome.

At this point you have reason to expect that many of the
subsequent tests also output strong results.

Now consider two alternative scenarios for the remaining 999,999 tests. In the first scenario, the remaining tests
produce $Z$ values that fit very well with the null, closely following a standard normal distribution; in the second
scenario a large proportion of the remaining tests, say 50 percent, show outcomes that lie outside of $[-4,4]$.

If your friend enquired after your analysis again, your
response would surely differ in the first scenario ("Oh, it didn't pan out so well after all") vs the second ("It went great"). Further,
in the first scenario, if your friend pressed you further about the results of the first test,
you would likely, I think, be inclined to put them down to chance. In contrast, in the second scenario, the first test turned out to be, as you hoped, a harbinger of good things to come, and in this scenario you would likely regard that test as likely corresponding to a true discovery.

The key point is that it is the *outcomes* of the tests, not the *number* of tests, that impacts interpretation of that first test.

(Some may by pondering whether the fact that you are about to perform another
999,999 tests should be considered pertinent in responding to your friend. Our view is that it is  irrelevant.
The standard frequentist framework would disagree, because
it requires the analyst to consider hypothetical repetitions
of the "experiment", and so the fact that the experiment
consists of a million tests is pertinent. However, this
argument is a distraction from the main point.)

Indeed, we believe that the practice of focussing on the *number* of tests performed is

Focussing on the number of tests performed can be
seen as an approximation.

The standard argument is that,
when performing multiple tests, some will be significant
just by chance.
